---
title: "Zopa LoanBook Analysis"
author: "Chiayi Yen"
date: "2016年12月6日"
output: slidy_presentation
---


## Prerequesite

```{r}
library(ggplot2)
library(dplyr)
library(magrittr)
library(ggthemes)
library(scales)
```


## Data Input

```{r}
df <- read.csv('data/data_for_loanbook_extract_2016-12-01.csv')
df %>% colnames()
df %>% head(1)
```


## Summary Statistics

* updated to 2016/12/1

```{r}
summary(df)
```


## Q:Growth trend over ten years

* Split Disbursal.date into year, month, and day
* Let's look at the total loan amount

```{r}
df <- df %>% mutate(
  yyyy = Disbursal.date %>% substr(1,4) %>% as.integer(),
  mm = Disbursal.date %>% substr(6,7) %>% as.integer(),
  dd = Disbursal.date %>% substr(9,10) %>% as.integer()
)

df %>% head(1)
```

```{r}
amt <- df %>% group_by(yyyy) %>% summarise(
loan_amount=sum(Original.Loan.Amount)
) 
amt %>% ggplot(aes(x=yyyy, y=loan_amount)) + geom_line()

```



## Q:Interest rate

```{r}
g <- df %>% 
ggplot(aes(x=Lending.rate, fill=factor(yyyy))) + 
geom_density(alpha=.3)

g + facet_wrap(~yyyy)
```

```{r}
df %>% group_by(yyyy) %>% 
summarise(mean=mean(Lending.rate),
median=median(Lending.rate),
sd=sd(Lending.rate))
```

## Q:What is the most popular loan term 

- Term ranges from 6 to 60
- What's the most popular product

```{r}
terms <- df %>% group_by(yyyy, Term) %>% summarise(
int=mean(Lending.rate),
counts=n())
terms %>% head()
```

```{r}
terms %>% 
ggplot(aes(x=yyyy, y=counts, fill=factor(Term))) + 
geom_bar(stat="identity", position="fill")  
```


## Q:term structure 

* price is not monotonically increasing in term period

```{r}
df %>% group_by(Term) %>% 
  summarise(int=mean(Lending.rate),
            counts=n()) %>% 
  ggplot(aes(x=Term, y=int)) + geom_line()

```

* Let's check the pattern over 10 years, increasing slope or decreasing slope?

```{r}
df %>% group_by(yyyy, Term) %>% 
summarise(int=mean(Lending.rate),
counts=n()) %>% 
ggplot(aes(x=Term, y=int)) + geom_line() + facet_wrap(~ yyyy)

```


## Q: default rate

```{r}
defl <- df %>% 
mutate(default= ifelse(Latest.Status=='Default', 1, 0)) %>% 
group_by(yyyy) %>% 
summarise(counts=n(), 
n_default=sum(default)/counts)
defl %>% head()
```

```{r}
defl %>% ggplot(aes(x=yyyy, y=n_default)) + geom_line() + geom_text(aes(label=round(100*n_default, 2)))

```


## Status analysis

```{r}
n_status <- df %>% 
group_by(yyyy, Latest.Status) %>% 
summarise(counts=n()) 
n_status %>% head()
```

```{r}
n_status %>% ggplot(aes(x=yyyy, y=counts, fill=factor(Latest.Status))) + 
geom_bar(stat="identity", position="fill")  
```


## Old Custom rate

```{r}
n_active <- df %>% filter(Latest.Status=='Active') %>% select(Encrypted.Member.ID) %>% unique() %>% nrow()
n_active/(df %>% select(Encrypted.Member.ID) %>% unique %>% nrow)
```
